Smoking and COVID Living Review (v7): a bayesian analysis

### 2020-08-26 reports/bayesian_report.Rmd
v7 final draft

## Load packages
* **Load packages**: load packages and useful scripts for the analysis
* **Load scripts**: We have written functions to handle much of the Bayesian analysis
* **Load Bayesian datasets**: The Bayesian approach relies on large simulated datasets from the observed data, for this report we will only present the results graphically from data we have simulated elsewhere. The scripts `bayes_scripts.R`, `bayesian_data_generation.R` and `bayesian_analysis.R` should be able to be run locally if you want to generate your own simulated data. Alternatively you can use the pre-generated data which is stored in the `data_clean\bayesian_models` folder in the github repository [here](https://github.com/DidDrog11/smoking_covid/tree/master) and then you can skip the `bayesian_data_generation.R` step.
```{r install_packages, include=FALSE}
library(brms)
library(ggplot2)
library(tidybayes)
library(readr)
library(dplyr)
library(ggridges)
library(glue)
library(stringr)
library(forcats)
library(here)
library(meta)
library(snakecase)
library(flextable)
library(googlesheets4)
library(linelist)
library(DT)
library(tidyr)
library(epitools)
```

>>>>

## Load packages
* **Load packages**: load packages and useful scripts for the analysis
* **Load scripts**: We have written functions to handle much of the Bayesian analysis
* **Load Bayesian datasets**: The Bayesian approach relies on large simulated datasets from the observed data, for this report we will only present the results graphically from data we have simulated elsewhere. The scripts `bayes_scripts.R`, `bayesian_data_generation.R` and `bayesian_analysis.R` should be able to be run locally if you want to generate your own simulated data. Alternatively you can use the pre-generated data which is stored in the `data_clean\bayesian_models` folder in the github repository [here](https://github.com/DidDrog11/smoking_covid/tree/master) and then you can skip the `bayesian_data_generation.R` step.
```{r install_packages, include=FALSE}
library(brms)
library(ggplot2)
library(tidybayes)
library(readr)
library(dplyr)
library(tidyr)
library(ggridges)
library(glue)
library(stringr)
library(forcats)
library(here)
library(meta)
library(snakecase)
library(flextable)
library(googlesheets4)
library(linelist)
library(DT)
library(epitools)
library(ggmap)
```
